---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# inih

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/inih)](https://CRAN.R-project.org/package=inih)
[![Codecov test coverage](https://codecov.io/gh/DyfanJones/inih/graph/badge.svg)](https://app.codecov.io/gh/DyfanJones/inih)
[![inih status badge](https://dyfanjones.r-universe.dev/inih/badges/version)](https://dyfanjones.r-universe.dev/inih)
<!-- badges: end -->

A simple wrapper of the [`inih`](https://github.com/benhoyt/inih) C library for reading and writing INI files in R.

## Installation

You can install the development version of inih like so:

Github:
``` r
remotes::install_github("dyfanjones/inih")
```

r-universe:
```r
install.packages("inih", repos = c("https://dyfanjones.r-universe.dev", "https://cloud.r-project.org"))
```

## Example

This is a basic example which shows you how to solve a common problem:

``` {r, read_ini}
library(inih)

demo_ini <- system.file("demo.ini", package = "inih")
read_ini(demo_ini)
```


``` {r, write_ini}
library(inih)

temp_file <- tempfile(fileext = ".ini")
# Create an example configuration list
config <- list(
  person = list(name = "John Doe", age = "30", city = "New York"),
  job = list(title = "Engineer", company = "ExampleCorp")
)

# Write the configuration to an INI file
write_ini(config, temp_file)

# Check the content of the created INI file
cat(readLines(temp_file), sep = "\n")

# clean up
unlink(temp_file)
```

## Benchmark:

```{r, benchmark} 
demo_ini <- system.file("demo.ini", package = "inih")
(bm <- bench::mark(
 inih::read_ini(demo_ini),
 ini::read.ini(demo_ini),
 relative = TRUE
))

ggplot2::autoplot(bm)
```

## Acknowledgements

This project uses the [`inih`](https://github.com/benhoyt/inih) library by Ben Hoyt, which is licensed under the BSD-3-Clause license. You can find the license text in the `inst/LICENSE-inih.txt` file.

